Irreducible Components and Dimension of the Springer Fiber of a Hook-Type Slodowy Slice

### 2024-09-03 paper.tex
up to section 9

\section{The Components of \texorpdfstring{\(S \times_\mathfrak{g} \widetilde{\mathcal{N}}\)}{S x\_g N}}\label{sxn_comps}
Recall from \cref{sn_iso} that 
\[S \times_\mathfrak{g} \widetilde{\mathcal{N}} \cong \{(A_{X,a,b}, U_\bullet, V_\bullet) : \forall i. \; XU_{i + 1} \subseteq U_i; \forall i. \; A_{X,a,b} V_{i + 1} \subseteq V_i\}.\]
We defined \(\pi : S \times_\mathfrak{g} \widetilde{\mathcal{N}} \to \mathcal{N}_m\) by \((A_{X,a,b}, U_\bullet, V_\bullet) \mapsto X\), and called \(\pi^{-1}(X)\) the \(n\)-Slodowy-slice Springer fiber at \(X\).
\begin{theorem}\label{springer_fiber_comps}
    \(\pi^{-1}(J(\lambda)) \cong \mathcal{P}_{J(\lambda)} \times X_\lambda\).
    Each irreducible component of \(\pi^{-1}(J(\lambda))\) has dimension \(\sum_{ij} \min(\lambda_i, \lambda_j)\).
\end{theorem}
\begin{proof}
    The isomorphism sends \((A_{X,a,b}, U_\bullet, V_\bullet)\) to \(((A_{X, a, b}, U_\bullet), V_\bullet)\).
    The irreducible components of \(\mathcal{P}_{J(\lambda)}\) are given by \cref{p_comps}.
    Those of \(X_\lambda\) are given by \cref{usual_springer_fiber}.
    Adding the dimensions gives 
    \[\sum_{i \leq j} \min(\lambda_i, \lambda_j) + \sum_{i < j} \min(\lambda_i, \lambda_j) = \sum_{ij} \min(\lambda_i, \lambda_j).\]
\end{proof}

Let \(\lambda\) be any partition of \(m\).
Let \(\GL_m \times \{I_n\}\) act on \(\pi^{-1}(J(\lambda))\) by conjugation; that is,
\[(P, I_n) \cdot (A_{X, a, b}, U_\bullet, V_\bullet) := \]
\[((P,I_n)A_{X,a,b}(P,I_n)^{-1},(P,I_n)U_\bullet, (P,I_n)V_\bullet).\]
Let 
\[K = \{(g, I_n) \in \GL_m \times \{I_n\} : gXg^{-1} = X\}.\]

@@

\begin{theorem}
    Every irreducible component of \(S \times_\mathfrak{g} \widetilde{\mathcal{N}}\) is the closure of some subvariety of the form \(\phi_\lambda(C_{\lambda,\beta} \times (\GL_m \times \{I_n\}))\), and the closure of each subvariety of this form is an irreducible component.
    Each has dimension \(m^2\).
\end{theorem}
\begin{proof}
    This is analogous to \cref{pwr_comps}; the only difference is the dimension calculation.
    This time, 
    \begin{align*}
        \dim \phi_\lambda(C_{\lambda, \beta} \times (\GL_m \times \{I_n\})) & = \\
        \dim C_{\lambda,\beta} + \dim \GL_m - \dim K & = \\
        \sum_{ij} \min(\lambda_i, \lambda_j) + m^2 - \sum_{ij} \min(\lambda_i, \lambda_j) & = \\
        m^2 & .
    \end{align*}
    The dimension of \(C_{\lambda, \beta}\) comes from \cref{pwr_comps}; the dimension of \(\GL_m\) is obvious; and the dimension of \(K\) comes from \cref{nilpotent_centralizer}.
\end{proof}

>>>>

\section{The Components of \texorpdfstring{\(S \times_\mathfrak{g} \widetilde{\mathcal{N}}\)}{S x\_g N}}\label{sxn_comps}
Recall from \cref{sn_iso} that 
\[S \times_\mathfrak{g} \widetilde{\mathcal{N}} \cong \{(A_{X,a,b}, U_\bullet, V_\bullet) : \forall i. \; XU_{i + 1} \subseteq U_i; \forall i. \; A_{X,a,b} V_{i + 1} \subseteq V_i\}.\]
We defined \(\pi : S \times_\mathfrak{g} \widetilde{\mathcal{N}} \to \mathcal{N}_m\) by \((A_{X,a,b}, U_\bullet, V_\bullet) \mapsto X\), and we called \(\pi^{-1}(X)\) the \(n\)-Slodowy-slice Springer fiber at \(X\).
\begin{theorem}\label{springer_fiber_comps}
    For any partition \(\lambda\) of \(m\), we have \(\pi^{-1}(J(\lambda)) \cong \mathcal{P}_{J(\lambda)} \times \mathcal{F}_{J(\lambda)}\).
    Each irreducible component of \(\pi^{-1}(J(\lambda))\) has dimension \(\sum_{ij} \min(\lambda_i, \lambda_j)\).
\end{theorem}
\begin{proof}
    The isomorphism sends \((A_{X,a,b}, U_\bullet, V_\bullet)\) to \(((A_{X, a, b}, U_\bullet), V_\bullet)\).
    The irreducible components of \(\mathcal{P}_{J(\lambda)}\) are given by \cref{p_comps}.
    Those of \(\mathcal{F}_{J(\lambda)}\) are given by \cref{usual_springer_fiber}.
    Adding the dimensions gives 
    \[\sum_{i \leq j} \min(\lambda_i, \lambda_j) + \sum_{i < j} \min(\lambda_i, \lambda_j) = \sum_{ij} \min(\lambda_i, \lambda_j).\]
\end{proof}

Let \(\lambda\) be any partition of \(m\), and let \(X = J(\lambda)\).
Let \(\GL_m \times \{I_n\}\) act on \(\pi^{-1}(J(\lambda))\) by change of basis; that is,
\[(P, I_n) \cdot (A_{X, a, b}, U_\bullet, V_\bullet) := \]
\[((P,I_n)A_{X,a,b}(P,I_n)^{-1},PU_\bullet, (P,I_n)V_\bullet).\]
Let 
\[K = \{(g, I_n) \in \GL_m \times \{I_n\} : gXg^{-1} = X\}.\]

@@

\begin{theorem}
    Every irreducible component of \(S \times_\mathfrak{g} \widetilde{\mathcal{N}}\) is the closure of a subvariety of the form \(\phi_\lambda(C_{\lambda,\beta} \times (\GL_m \times \{I_n\}))\), and the closure of each subvariety of this form is an irreducible component.
    Each has dimension \(m^2\).
\end{theorem}
\begin{proof}
    This is analogous to \cref{pwr_comps}; the main difference is the dimension calculation.
    This time, 
    \begin{align*}
        \dim \phi_\lambda(C_{\lambda, \beta} \times (\GL_m \times \{I_n\})) & = \\
        \dim C_{\lambda,\beta} + \dim \GL_m - \dim K & = \\
        \sum_{ij} \min(\lambda_i, \lambda_j) + m^2 - \sum_{ij} \min(\lambda_i, \lambda_j) & = \\
        m^2 & .
    \end{align*}
    The dimension of \(C_{\lambda, \beta}\) comes from \cref{springer_fiber_comps}; the dimension of \(\GL_m\) is obvious; and the dimension of \(K\) comes from \cref{nilpotent_centralizer}.
\end{proof}
